### 2021-09-29 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betadiversity_response@36af1046e0f58287231a230fcb53eec08dcd4896 🚀

The approach to quantifying the difference between pairs of networks
established in Poisot \emph{et al.} (2012) is a simple extension of the
overall method by Koleff \emph{et al.} (2003) for species dissimilarity
baed on presence-absence data. The objects to compare, \(X_1\) and
\(X_2\), are partitioned into three values, \(a = |X_1 \cup X_2|\),
\(b = |X_2 \setminus X_1|\), and \(c = |X_1 \setminus X_2|\), where
\(|x|\) is the cardinality of set \(x\), and \(\setminus\) is the set
substraction operation. In the perspective of species composition
comparison, \(X_1\) and \(X_2\) are the sets of species in either
community, so that if \(X_1 = \{x, y, z\}\) and
\(X_2 = \{v, w, x, y\}\), we have \(X_1 \cup X_2 = \{v, w, x, y, z\}\),
\(X_1 \cap X_2 = \{x, y\}\), \(X_2 \setminus X_1 = \{v, w\}\), and
\(X_1 \setminus X_2 = \{z\}\). The core message of Koleff \emph{et al.}
(2003) is that the overwheling majority of measures of
\(\beta\)-diversity can be re-expressed as functions that operate on the
cardinality (number of elements) of these sets.

>>>>

The approach to quantifying the difference between pairs of networks
established in Poisot \emph{et al.} (2012) is a simple extension of the
overall method by Koleff \emph{et al.} (2003) for species dissimilarity
baed on presence-absence data. The objects to compare, \(X_1\) and
\(X_2\), are partitioned into three values, \(a = |X_1 \cup X_2|\),
\(b = |X_2 \setminus X_1|\), and \(c = |X_1 \setminus X_2|\), where
\(|\dot|\) is the cardinality of set \(\dot\) (the number of elements it
contains), and \(\setminus\) is the set substraction operation. In the
perspective of species composition comparison, \(X_1\) and \(X_2\) are
the sets of species in either community, so that if
\(X_1 = \{x, y, z\}\) and \(X_2 = \{v, w, x, y\}\), we have
\(X_1 \cup X_2 = \{v, w, x, y, z\}\), \(X_1 \cap X_2 = \{x, y\}\),
\(X_2 \setminus X_1 = \{v, w\}\), and \(X_1 \setminus X_2 = \{z\}\). The
core message of Koleff \emph{et al.} (2003) is that the overwheling
majority of measures of \(\beta\)-diversity can be re-expressed as
functions that operate on the cardinality of these sets -- this allows
to focus on the number of unique and common elements, as outlined in
fig.~\ref{fig:conceptual}.
